%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Thank you Jake Gutierrez
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-7pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5.3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\vspace{-26pt}
\begin{center}
    \textbf{\Huge \scshape Joshua Gustaveson} \\ \vspace{1pt}
    \small 801-600-0229 $|$ \href{mailto:joshgus@umich.edu}{\underline{joshgus@umich.edu}} $|$ 
    \href{https://linkedin.com/in/joshuagustaveson}{\underline{linkedin.com/in/joshuagustaveson}}  % $|$
    %\href{https://github.com/JoshGus}{\underline{github.com/JoshGus}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan - Ann Arbor}{Aug. 2023 -- Apr. 2027 (Anticipated)}
      {Bachelors in Engineering - Computer Science} {Ann Arbor, MI}
      % PRESENTED INFORMATION FOR THE UI TEAM???
      \resumeItemListStart
        \resumeItem{Relevant Courses: Data Structures \& Algorithms, Discrete Math, Linear Algebra, Technical Communication, }
        \resumeItem{William J. Branstrom Freshman Prize, 2023 University Honors}
      \resumeItemListEnd
\resumeSubHeadingListEnd
%GAPS

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Classroom Tech Maintenance Technician}{May 2025 -- Current}
      {University of Michigan Computer Aided Engineering (CAEN) Services}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{Maintained instructional tech across 70+ classrooms, including AV systems, control panels, and desktop stations}
        \resumeItem{Balanced service tickets and scheduled tasks to ensure minimal downtime for instructional spaces}
        \resumeItem{Collaborated with CAEN engineers to deploy equipment and troubleshoot hardware/software failures}
      \resumeItemListEnd
      
    \resumeSubheading
      {Website Manager / Administrative Assistant}{Mar. 2025 -- Current}
      {Leinweber Institute for Theoretical Physics (LITP)}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{Maintained the institute’s websites, ensuring up-to-date event listings, research pages, and faculty profiles}
        \resumeItem{Organized communications, scheduling, and logistics for lectures, conferences, and workshops}
        \resumeItem{Performed administrative operations, including calendar management, procurement, and documentation}
      \resumeItemListEnd
      
    \resumeSubheading
      {Frontend Development Lead}{Apr. 2024 -- Sep. 2024}
      {Slow (AI enabled Mental Health Application)}{Ogden, UT}
      % PRESENTED INFORMATION FOR THE UI TEAM???
      \resumeItemListStart
        \resumeItem{Led development of Swift based mobile application, utilizing Scrum framework to manage UI/UX issues and goals}
        \resumeItem{Facilitated User Acceptance Testing, gathering stakeholder feedback to iteratively refine features before launch}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Full Stack Developer}{Jun. 2020 -- Sep. 2023}
      {Dubai Association of Varsity Sports}{Dubai, UAE}
      \resumeItemListStart
        \resumeItem{Produced a dynamic website for the Dubai varsity basketball league using HTML, CSS, JavaScript, PHP, and MySQL to showcase statistics for 200+ players, reaching \( \ 500+ \) monthly website viewers.}
        \resumeItem{Engaged and facilitated meetings with prospective corporate partners to sponsor community events}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%GAPS
%-----------PROJECTS-----------
\section{Relevant Projects} 
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Machine Learning Post Classifier} $|$ \emph{C++, Visual Studio Code, Git}}{Jan. 2024 -- May. 2024}
          \resumeItemListStart
            \resumeItem{Constructed a Naive Bayes Machine Learning Model labeling new Piazza posts based on previous labeled data.}
            \resumeItem{Utilized natural language processing techniques to parse and analyze over 100 CSV files, allowing the model to efficiently learn and continuously improve associations between keywords and labels.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Data Transmission Error Detection \& Correction Instructional Aid} $|$ \emph{C++}}{Aug. 2023 -- Nov. 2023}
          \resumeItemListStart
            \resumeItem{Enhanced data communication reliability in a simulated environment by designing additional hybrid algorithms capable of encoding and decoding error-resilient messages}
            \resumeItem{Developed an instructional aid to display the effects of data transmission error and the limitations of utilizing common methods of data integrity protection}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Multiplayer Online Board Game} $|$ \emph{C\#, Unity}}{Sep. 2021 -- Jul. 2023}
          \resumeItemListStart
            \resumeItem{Built a Board Game application using C\# and Unity employing a Test-Driven Development methodology that integrates real-time connectivity and a database backed account system}
            \resumeItem{Led stakeholder interviews and user testing sessions, surveying target demographic to capture concept feedback}
            \resumeItem{Created a 100-page design development document, including research to enhance accessibility features for visually impaired users}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%GAPS


%-----------Leadership-----------
\section{Leadership and Extracurriculars} 
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Michigan Task-Based Robotics Project Team} $|$ \emph{Programming Team Member}}{Aug. 2024 -- Current}
          \resumeItemListStart
            \resumeItem{Worked in a team to program autonomous navigation algorithms to perform tasks in dynamic environments}
            \resumeItem{Collaborated with mechanical team to integrate software solutions with a variety of sensors and motor systems}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Taekwondo} $|$ \emph{1st Degree Black Belt / Collegiate Athlete}}{Aug. 2015 -- Current}
          \resumeItemListStart
            \resumeItem{Led training sessions for new members, helping them improve and understand the principles of Taekwondo}
            
            \resumeItem{Competed in the MIT and Princeton 2024 Collegiate Tournaments as part of the University of Michigan's A1 team}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Living Arts Engine (LAE)} $|$ \emph{Learning Community Member}}{Aug. 2023 -- Jul. 2024}
          \resumeItemListStart
            \resumeItem{Competed in the LAE MakeAThon producing a dynamic installation artwork on the relationship between Art and Artificial Intelligence. Achieved first place and won cash prize.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%GAPS
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Frameworks}{: Python, C, C++, C\#, SQL, PHP, HTML, CSS, Swift, Django} \\
     \textbf{Developer Tools and Skills}{: Git, VSCode, XCode, Microsoft Office, Google Suite, Unity, Blender, Fusion 360, Figma} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, scikitlearn} \\ }
     }
 \end{itemize}


%-------------------------------------------
\end{document}
